---
title: "Class Project: Multiple Linear Regression on Market Share data"
author: "Ashwin Rathore"
date: "07/09/2021"
output:
  pdf_document: default
  html_document: default
---

 Importing data from market_share.xlsx file and creating a dataframe.
```{r}
library("readxl")
ms <- read_excel("market_share.xlsx")
ms =within(ms, rm(idnum))
ms$month <- as.numeric(as.factor(ms$month))
ms
```

Applying linear regression between market share and the rest of the covariates one by one to find the relationship.
```{r}
lm.price <- lm(ms$marketshare ~ ms$price, data = ms)
summ.price <- summary(lm.price)
summ.price

lm.gnrpoints <- lm(ms$marketshare ~ ms$gnrpoints, data = ms)
summ.gnrpoints <- summary(lm.gnrpoints)
summ.gnrpoints

lm.discount <- lm(ms$marketshare ~ ms$discount, data = ms)
summ.discount <- summary(lm.discount)
summ.discount

lm.promotion <- lm(ms$marketshare ~ ms$promotion, data = ms)
summ.promotion <- summary(lm.promotion)
summ.promotion

lm.month <- lm(ms$marketshare ~ ms$month, data = ms)
summ.month <- summary(lm.month)
summ.month

lm.year <- lm(ms$marketshare ~ ms$year, data = ms)
summ.year <- summary(lm.year)
summ.year
```

<!-- Plotting estimated regression function: -->

<!-- ```{r} -->
<!-- plot(senic$infection_risk ~ senic$length_of_stay) -->
<!-- abline(0.74430  , 0.37422) -->
<!-- abline(lmsenic1) -->

<!-- plot(senic$ava_facilities ~ senic$length_of_stay) -->
<!-- abline(15.8795  , 2.8274) -->
<!-- abline(lmsenic2) -->

<!-- plot(senic$xray_ratio ~ senic$length_of_stay) -->
<!-- abline(44.2440  , 3.8747) -->
<!-- abline(lmsenic3) -->
<!-- ``` -->

Building the “best" regression model for Y

```{r}
library(leaps)
b <- regsubsets(ms$marketshare ~., data = ms, nvmax=6)
rs <- summary(b)
rs$rsq
plot(rs$rss,xlab='No. of Variables',ylab='RSS',type='l')
plot(rs$cp,xlab='No. of Variables',ylab='Cp',type='l')
which.min(rs$cp)
points(3,rs$cp[3],pch=19,col='red')
plot(b,scale='Cp')

```
The best model according to both R^2 and Cp is the one that uses price, discount, promotion, month and year. We can remove teh gnrpoints as it does not relate much with the market share.

Fitting the model.


```{r}
ms_data <- data.frame(ms$price, ms$discount, ms$promotion, ms$month, ms$year)
library(VIF)
vif(ms_data)
```
A commonly used practice is if a VIF is > 10, you have high multicollinearity. In our case, with values around 0, we are in good shape, and can proceed with our regression.

– Outliers and influential points

```{r}
lmms <- lm(ms$marketshare ~ ms$price+ ms$discount+ ms$promotion+ ms$month+ ms$year, data = ms)
plot(lmms, 5)
```
In the Residuals vs Leverage plot, no influential points are outside the Cook’s distance lines (a red dashed
line). Thus we can assume there are no outliers in the data.


– Appropriateness of predictors (i.e., is any transformation of predictors necessary?)

```{r}
plot(lmms, 1)
```

<!-- There is no pattern in the residual plot in the graph and the red line is almost horizontal around 0. Hence -->
<!-- we can assume the linear relationship between ACT and GPA (except 47 and 112 which are outliers). -->

<!-- – Normality of residuals -->


```{r}
plot(lmms, 2)
```

<!-- In Normal QQ plot, all the points fall approximately along this reference line except 2 points as we noticed, 47 and 112(which are outliers), so we can assume normality. -->
<!-- plot(lmgpa, 3) -->

– Constant variance of residuals

```{r}
plot(lmms, 3)
```
<!-- It can be seen in the Scale-location plot that the variability (variances) of the residual points is constant -->
<!-- with the value of the fitted outcome variable, suggesting constant variances in the residuals errorsThus we -->
<!-- can see Homogeneity of variance(except 47 and 112 which are outliers). . -->



<!-- 7. Provide an intuitive interpretation of your final model. In other words, explain your findings to me as if -->
<!-- I have a minimal working knowledge of statistics. -->

<!-- Ans: In the dataset, we wanted to know if Average length of stay in a hospital (Y) is related to infection risk, -->
<!-- available facilities and services, and routine chest X-ray ratio or not. If yes, which combination of these factors are important to affect the Y. Thus we built a regression model to check the dependency of Y on these factors. We found out that the combination of all 3 of these factors plays a crucial role in obtaining Y and thus we made a model that can predict Y on the basis of these 3 variables. Also, we found out some outliers in our analysis (record 47 and 112 ) which can be removed to make data more coherent for prediction. -->

















